Interoperable

### 2019-11-26 report/cloud-course-final-report/Article.tex
Add figures

\section*{Other benchmarks}
For the other benchmarks, interoperable application mainly leverages the fields that exist within the corresponding configuration files per container. For example,
to implement \textbf{5.4, 5.7, 5.8, 5.9, 5.12, 5.13, 5.14, 5.15, 5.16, 5.17, 5.18, 5.20 and 5.25} on Docker, we use Hostconfig.json file for a given container. This file
is created and stored per container in : \textit{/var/lib/docker/containers/} \textit{<container-id>/hostconfig.json}. To implement \textbf{5.3, 5.5, 5.21, 5.24} on docker, our application uses config.json under \textit{/run/containerd/io.containerd.runtime.v1.linux/moby/} \textit{<container-id>/config.json}.
\\
For crio, interoperable application implements \textbf{5.3, 5.4, 5.5, 5.7, 5.8, 5.9, 5.12, 5.13, 5.15, 5.16, 5.17, 5.20, 5.21, 5.24} using the config.json file per container. For crio this file is found from \textit{/var/lib/containers/storage/overlay-containers/}\textit{<container-id>/userdata/config.json}
\\

Containerd....

\section*{Bibliography}

>>>>

\section*{Other benchmarks}
For the other benchmarks, interoperable application mainly leverages the fields that exist within the corresponding configuration files per container. For example,
to implement \textbf{5.4, 5.7, 5.8, 5.9, 5.12, 5.13, 5.14, 5.15, 5.16, 5.17, 5.18, 5.20 and 5.25} on Docker, we use Hostconfig.json file for a given container. This file
is created and stored per container in : \textit{/var/lib/docker/containers/} \textit{<container-id>/hostconfig.json}. To implement \textbf{5.3, 5.5, 5.21, 5.24} on docker, our application uses config.json under \textit{/run/containerd/io.containerd.runtime.v1.linux/moby/} \textit{<container-id>/config.json}.
\\

For crio, interoperable application implements \textbf{5.3, 5.4, 5.5, 5.7, 5.8, 5.9, 5.12, 5.13, 5.15, 5.16, 5.17, 5.20, 5.21, 5.24} using the config.json file per container. For crio this file is found from \textit{/var/lib/containers/storage/overlay-containers/}\textit{<container-id>/userdata/config.json}
\\

For Containerd, interoperable application implements \textbf{5.3, 5.4, 5.5, 5.17, 5.24, 5.25} using the config.json file per container.
For containerd, this file is found from \textit{/run/containerd/io.containerd.runtime.v2.task/default//} \textit{<container-id>/config.json}.
Interoperable application implements \textbf{5.12, 5.15, 5.16, 5.20, 5.21} using the state.json file per container.
For containerd, this file is found from \textit{/run/containerd/runc/default/}\textit{<container-id>/state.json}
\section*{Appendix}

\begin{figure*}
    \caption{Docker.}
    \centering
      \includegraphics[width=\textwidth,height=10cm]{figures/docker}
  \end{figure*}

  \begin{figure*}
    \caption{CRIO.}
    \centering
      \includegraphics[width=\textwidth,height=10cm]{figures/crio}
  \end{figure*}

  \begin{figure*}
    \caption{Containerd}
    \centering
      \includegraphics[width=\textwidth,height=10cm]{figures/containerd}
  \end{figure*}
\section*{Bibliography}
